---
output: github_document
always_allow_html: true
---

<!-- This file is used to create README.md
Note that the README.md document may need updating to change
'\<0.001' to '<0.001'. 
-->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

```

# BiostatsUHNplus

The goal of BiostatsUHNplus is to house publicly available code functions and snippets (some with multiple package dependencies) 
used by Biostatistics@UHN.

Many of these functions build upon the features of **reportRmd**.

## Installation

You can install the development version of BiostatsUHNplus from [GitHub](https://github.com/) with:


``` r
# install.packages("devtools")
devtools::install_github("biostatsPMH/BiostatsUHNplus")
```

## Documentation

[Online Documentation](https://biostatsPMH.github.io/BiostatsUHNplus/)

## Example

### A wrapper for the as.numeric function. Prints entries that fail to parse instead of throwing uninformative error

```{r example1}
library(BiostatsUHNplus);
z <- as_numeric_parse(c(1:5, "String1",6:10,"String2"))
z

```


### Summary statistics by patient ID nested in cohort, stratified by overall survival status

Use summary output and unnested or nested p-value with caution!

```{r example2}
library(reportRmd);
library(BiostatsUHNplus);
data("pembrolizumab");
#str(pembrolizumab);

rm_covsum_nested(data = pembrolizumab, id = c("id", "cohort"), 
  covs = c("age", "sex", "l_size", "pdl1", "tmb", 
  "baseline_ctdna", "change_ctdna_group", "orr", "cbr", "os_time",
  "pfs_status", "pfs_time"), maincov = "os_status");

```


