---
output: github_document
always_allow_html: true
---

<!-- This file is used to create README.md
Note that the README.md document may need updating to change
'\<0.001' to '<0.001'. 
-->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

```

# BiostatsUHNplus

The goal of **BiostatsUHNplus** is to house publicly available code functions and snippets (some with multiple package dependencies) 
used by [Biostatistics@UHN](https://www.biostatspm.com/) in Toronto, Canada.

Many of these functions build upon the features of [**reportRmd**](https://github.com/biostatsPMH/reportRmd).

## Installation

If using the main branch of **reportRmd**, you can install the main version of **BiostatsUHNplus** from [GitHub](https://github.com/) with:


``` r
# install.packages("devtools")
devtools::install_github("biostatsPMH/BiostatsUHNplus", ref="main")
```

If using the development branch of **reportRmd**, you can install the development version (option to include effect size in nested summaries) of **BiostatsUHNplus** from [GitHub](https://github.com/) with:


``` r
# install.packages("devtools")
devtools::install_github("biostatsPMH/BiostatsUHNplus", ref="development")
```

## Documentation

[Online Documentation](https://biostatsPMH.github.io/BiostatsUHNplus/)

## Example

### A wrapper for the as.numeric function. Prints entries that fail to parse instead of throwing uninformative error

```{r example1}
library(BiostatsUHNplus);
z <- as_numeric_parse(c(1:5, "String1",6:10,"String2"))
z

```


### Summary statistics by patient ID nested in cohort, stratified by overall survival status

Use summary output and unnested or nested p-value with caution!

```{r example2}
library(reportRmd);
library(BiostatsUHNplus);
data("pembrolizumab");
#str(pembrolizumab);

rm_covsum_nested(data = pembrolizumab, id = c("id", "cohort"), 
  covs = c("age", "sex", "l_size", "pdl1", "tmb", 
  "baseline_ctdna", "change_ctdna_group", "orr", "cbr", "os_time",
  "pfs_status", "pfs_time"), maincov = "os_status");

```



### Outputs three DSMB-CCRU AE summary tables in Excel format per UHN template

Uses addendum fake study data. DSMB-CCRU AE summary tables in below code example can be found in the *dsmb_ccru_tables* folder of **BiostatsUHNplus** package.

```{r example3}
library(reportRmd);
library(BiostatsUHNplus);
data("enrollment", "demography", "ineligibility", "ae");

## This does summary for all participants;
dsmb_ccru(protocol="EXAMPLE_STUDY",setwd=".",
          title="Phase X Study to Evaluate Treatments A-D",
          comp=NULL,pi="Dr. Principal Investigator",
          presDate="30OCT2020",cutDate="31AUG2020",
          boundDate=NULL,subjID="Subject",subjID_ineligText=c("New Subject","Test"),
          baseline_datasets=list(enrollment,demography,ineligibility),
          ae_dataset=ae,ineligVar="INELIGIBILITY_STATUS",ineligVarText=c("Yes","Y"),
          genderVar="GENDER_CODE",enrolDtVar="ENROL_DATE_INT",ae_detailVar="ae_detail",
          ae_categoryVar="ae_category",ae_severityVar="AE_SEV_GD_STD",
          ae_onsetDtVar="AE_ONSET_DT_INT",ae_detailOtherText="Other, specify",
          ae_detailOtherVar="CTCAE5_LLT_NM",ae_verbatimVar="AE_VERBATIM_TRM_TXT",
          numSubj=NULL)

## This does summary for each cohort;
dsmb_ccru(protocol="EXAMPLE_STUDY",setwd=".",
          title="Phase X Study to Evaluate Treatments A-D",
          comp="COHORT",pi="Dr. Principal Investigator",
          presDate="30OCT2020",cutDate="31AUG2020",
          boundDate=NULL,subjID="Subject",subjID_ineligText=c("New Subject","Test"),
          baseline_datasets=list(enrollment,demography,ineligibility),
          ae_dataset=ae,ineligVar="INELIGIBILITY_STATUS",ineligVarText=c("Yes","Y"),
          genderVar="GENDER_CODE",enrolDtVar="ENROL_DATE_INT",ae_detailVar="ae_detail",
          ae_categoryVar="ae_category",ae_severityVar="AE_SEV_GD_STD",
          ae_onsetDtVar="AE_ONSET_DT_INT",ae_detailOtherText="Other, specify",
          ae_detailOtherVar="CTCAE5_LLT_NM",ae_verbatimVar="AE_VERBATIM_TRM_TXT",
          numSubj=NULL)
```


